explore_basis

### 2020-05-31 source/explore_basis.Rmd
update explore_basis

load(here::here("data/holes_1d_geo.rda"))
load(here::here("data/holes_1d_geo_polish.rda"))
load(here::here("data/holes_2d_geo.rda"))
load(here::here("data/holes_2d_geo_polish.rda"))
```

@@

```{r}
holes_1d_geo %>% explore_proj_pca() 
```

@@

```{r}
glb_obj <- bind_rows(holes_1d_geo, holes_1d_geo_polish)

combined %>% 
  ggplot(aes(x = PC1, y = PC2, col = method)) +
  geom_point() +
  geom_point(data = combined %>% filter(method == "search_geodesic")) +
  #stat_density(aes(fill = after_stat(nlevel)), geom = "polygon", alpha = 0.5) +
  theme(aspect.ratio = 1)
```

@@

```{r}
combined %>% 
  ggplot(aes(x = PC1, y = PC2, col = as.factor(alpha))) +
  geom_point() +
  geom_point(data = combined %>% filter(method == "search_geodesic")) +
  #stat_density(aes(fill = after_stat(nlevel)), geom = "polygon", alpha = 0.5) +
  theme(aspect.ratio = 1)
```

@@

```{r}
combined %>% filter(alpha < 0.03) %>% 
  ggplot(aes(x = PC1, y = PC2, col = as.factor(alpha))) +
  geom_point() +
  geom_point(data = combined %>% filter(method == "search_geodesic")) +
  #stat_density(aes(fill = after_stat(nlevel)), geom = "polygon", alpha = 0.5) +
  theme(aspect.ratio = 1)
```

```{r}
combined %>% filter(info == "polish_best") %>% dplyr::select(index_val, alpha, loop)
```

>>>>

load(here::here("data/holes_1d_geo.rda"))
load(here::here("data/holes_1d_geo_polish.rda"))
load(here::here("data/holes_1d_geo_polish_default_alpha.rda"))
load(here::here("data/holes_2d_geo.rda"))
load(here::here("data/holes_2d_geo_polish.rda"))
```

@@

```{r}
holes_1d_geo %>% explore_proj_pca(col = info) 
```

@@

```{r}
bind_rows(holes_1d_geo, holes_1d_geo_polish_default_alpha) %>% 
  explore_proj_pca(col = method)
```

@@

```{r}
bind_rows(holes_1d_geo, holes_1d_geo_polish_default_alpha) %>% 
  explore_proj_pca(col = as.factor(alpha))
```

@@

```{r}
bind_rows(holes_1d_geo, holes_1d_geo_polish) %>% 
  explore_proj_pca(col = as.factor(alpha))
```
